\section{Work Experience}%-----------WORK EXPERIENCE-----------
% if you have been employed, do volunteer activities, or have held other formal or informal jobs, you can list them here.   
\resumeSubHeadingListStart

     \resumeSubheading
      {Research Assistant - University of British Columbia }{May-July 2024}
      {Sensorimotors Lab}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Processing 3D Human Data Capture for Lululemon}
        \small\resumeItem{Deformation fields were used to interpolate shapes between periodically captured humans}
        \resumeItemListEnd
    \resumeSubheading
      {Research Assistant - University of British Columbia }{January – May 2024}
      {Visual AI for Humans Lab and Sensorimotors Lab}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Executed a 3D Capture Dataset of Humans under Dr. Helge Rhodin and Dr. Dinesh Pai}
        \resumeItem{The project offered ground truth meshes of humans, a calibrated tri-camera setup, and evaluated the leading shape estimation models}
        \resumeItemListEnd
        
    \resumeSubheading
      {Software Developer - Mott Macdonald Canada Limited}{May 2021 - August 2023}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Implementation of potential traffic collision avoidance solution using computer vision-based predictive algorithms and vehicle tracking.}
        \resumeItem{Co-developed a Geometry Data Management firmware to attach archivable, nested metadata to engineering models.}
        \resumeItemListEnd

    \resumeSubheading
      {Research Assistant - University of British Columbia }{January – May 2021}
      {Visual AI for Humans Lab}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Researched Direct Linear transformations and their application in human pose estimation under Dr. Helge Rhodin.}
        \resumeItem{Developed human tracking scripts through visual computation to research the accuracy and robustness of my closed-form implementation.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer Co-op - Mott Macdonald Canada Limited }{May – December 2019}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Developed for Safestroll - A smart city app to guide kids in safely navigating between school and home.}
        \resumeItem{Designed and implemented a .NET library to facilitate functional independence between Station-based and modeling geometry.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer Co-op - Mott Macdonald Canada Limited}{January – August 2019}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Implemented novel meshing algorithms to achieve interoperability within engineering design software.}
        \resumeItemListEnd

    \resumeSubheading
      {Project Lead - University of British Columbia }{January 2020 – May 2020}
      {Emerging Media Labs}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Project Lead for 3D Metabolism – an Augmented Reality (AR) solution to aid Biochemistry and Microbiology students visualize metabolism.}
        \resumeItem{Designed an AR app SynesthesiAR to map Fourier Transform pitch detection into visuals.}
        \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------SKILLS-----------

