\section{Work Experience}%-----------WORK EXPERIENCE-----------
% if you have been employed, do volunteer activities, or have held other formal or informal jobs, you can list them here.   
\resumeSubHeadingListStart

    \resumeSubheading
      {Research Assistant - University of British Columbia }{August 2023 – Present}
      {Visual AI for Humans Lab and Sensorimotors Lab}{Vancouver, BC, Canada }
      \resumeItemListStart
        % \small\resumeItem{Processing 3D Human Data Capture for Lululemon}
        \small\resumeItem{Leveraged deformation fields to interpolate shapes between periodically captured humans to be used for a project with a sportswear company }
        \small\resumeItem{Independently executed a 3D Capture Dataset of Humans under Dr.\ Helge Rhodin and Dr.\ Dinesh Pai.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Software Developer - Mott MacDonald}{May 2021 - August 2023}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Ensured technical support and high availability of engineering application evironments through organized and automated GitHub workflows, Azure Function Apps and GitHub Functions}
        \small\resumeItem{Collaborated with data architects and designed project management dashboards using Microsoft PowerBI.\@ The project required active collaboration with stakeholders, requirements gathering, comprehensive documentation, solutioning their dynamic requirements through scrum practices and agile workflow}
        \small\resumeItem{Individually hosted and owned multiple Azure DevOps microservices through Docker, PostgreSQL, Redis and Azure containers. This was used by core engineering team for Toronto Transit Commission Scarborough Extension Project. Project was actively maintained through both remediation and root cause analysis, ensuring high availability}
        \small\resumeItem{Implemented potential traffic collision avoidance solution using computer vision-based predictive algorithms and vehicle tracking. This also included generating the front-end through ViewJS}
        \small\resumeItem{Co-developed a Geometry Data Management API to attach archivable metadata to engineering models using contemporary software development practices}
        \small\resumeItem{Organized and collaborated on multiple digital advancement initiatives, developing system integrations, automating and streamlining release pipelines through Git and Azure tools, and documenting best developement practices}
        \resumeItemListEnd

    \resumeSubheading
      {Research Assistant - University of British Columbia }{January – May 2021}
      {Visual AI for Humans Lab}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Researched Direct Linear transformations and their application in human pose estimation under Dr. Helge Rhodin.}
        \resumeItem{Developed human tracking scripts through visual computation to research the accuracy and robustness of my closed-form implementation.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer Co-op - Mott MacDonald }{May – December 2019}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Demonstrated quick requirement assimilation and solution development by generating and presenting novel visualizations for stress testing in SAP applications within 2 weeks of project bidding. }
        \resumeItem{Configured and enhanced existing engineering environments like Autodesk and Rhino through designing and implementing .NET libraries, thereby facilitating functional independence between Station-based and modeling geometry.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer Co-op - Mott MacDonald}{January – August 2019}
      {Digital Advancement Network}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Implemented novel meshing algorithms to achieve interoperability within engineering modeling and CAD-based design software. These implementations were meticulously documented and presented to engineers and stakeholders }
        \small\resumeItem{Delivered new solutions and enhancements using existing low-code tools like Powershell automations scripts to control software duplication in the company}

        \resumeItemListEnd

    \resumeSubheading
      {Project Lead - University of British Columbia }{January 2020 – May 2020}
      {Emerging Media Labs}{Vancouver, BC, Canada }
      \resumeItemListStart
        \small\resumeItem{Lead 3D Metabolism – an Augmented Reality (AR) solution to aid Biochemistry and Microbiology students visualize metabolism.}
        \resumeItem{Designed an AR app SynesthesiAR to map Fourier Transform pitch detection into visuals.}
        \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------SKILLS-----------

